Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2001-01-01 paper.tex
Matt's edits through p. 15: move acknowledgements
Fix sign error in equations in appendix

We follow
\cite{brue1985-core_collapse} and \cite[Sec.~4]{shib2011-truncated_moment}
by separating these processes into four categories:
\begin{equation}
  \label{eqn:four_sources}
  C[f] \equiv C_{\rm AE} + C_{\rm SE} + C_{\rm SI} + C_{\rm PP},
\end{equation}
representing charged-current absorption and emission, elastic scattering,
inelastic scattering, and the thermal pair processes of annihilation and
production. In this work, however, we only treat absorption/emission
and elastic scattering.
We seek to write each collision source linear in $f$:
\begin{align}
  \label{eqn:sources_cae}
  C_{\rm AE}
  &= \mathscr{E}_{\rm AE} + \mathscr{K}_{\rm AE}\, f, \\
  \label{eqn:sources_cse}
  C_{\rm SE}
  &= \mathscr{E}_{\rm SE} + \mathscr{K}_{\rm SE}\, f.
\end{align}

>>>>

We follow
\cite{brue1985-core_collapse} and \cite[Sec.~4]{shib2011-truncated_moment}
by separating these processes into four categories:
\begin{equation}
  \label{eqn:four_sources}
  C[f] \equiv C_{\rm AE} + C_{\rm SE} + C_{\rm SI} + C_{\rm PP},
\end{equation}
representing charged-current absorption and emission, elastic scattering,
inelastic scattering, and the thermal pair processes of annihilation and
production. In this work, however, we only treat absorption/emission
and elastic scattering.
We seek to write each collision source linear in $f$:
\begin{align}
  \label{eqn:sources_cae}
  C_{\rm AE}
  &= \mathscr{E}_{\rm AE} - \mathscr{K}_{\rm AE}\, f, \\
  \label{eqn:sources_cse}
  C_{\rm SE}
  &= \mathscr{E}_{\rm SE} - \mathscr{K}_{\rm SE}\, f.
\end{align}
